%! TeX root = ./main.tex
\section{Review}
\label{sec:Review}
\begin{itemize}
	\item $\lambda$-$\pi$ theorem, monotone class theorem, typical method.
	\item  $\sigma$-finite measures on semi-ring can be uniquely
		extended to the $\sigma$-algebra.
		The uniqueness only requires $\pi$-system.
	\item Different convergence of functions:
		a.u., a.e./a.s., $\mu$, $L^p$, $(w)L^p$.
	\item The construction of integrals, check if the integral exists.
	\item The linearity, monotonicity of integrals and their conditions.
	\item The three limit theorems and their proofs,
		the countable additivity of indefinite integrals.
	\item Substitution formula of integrals, expectations of random variables.
	\item $L^p$ space is a Banach space, Holder's \& Minkowski's inequality.
	\item Equivalent conditions of $L^p$ convergence and weak $L^p$ convergence.
	\item In probability space, the inckusion relations of $L^p$'s,
		definition and equivalent conditions of uniformly integrable.
	\item Definitions of signed measures, absolute continuity and mutual singularity.
	\item Hahn decomposition, Jordan decomposition, the ``maximum'' sets.
	\item R-N derivatives $\frac{\dd \varphi}{\dd \mu}$, the ``maximum'' function.
	\item Absolutely continuous signed measures = indefinite integrals,
		R-N derivatives = functions being integrated.
	\item Lebesgue decomposition, taking R-N derivatives with respect to $\varphi + \mu$.
	\item Conditional expectations $f^* = E(f|\mathscr{G})$, where
		the integral of $f$ exists.
	\item Two properties: (1) $f^*\in \mathscr{G}$,
		(2) $Ef^*\ii_A = Ef\ii_A, \forall A\in \mathscr{G}$.
	\item Linearity of conditional expectations, $f\in \mathscr{G}$ vs.
		$f$ and $\mathscr{G}$ are independent.
	\item The use of $\lambda$- $\pi$ theorem and typical method!
	\item Multiple expectation formula, limit theorems of conditional expectations.
	\item Regular conditional distribution of given values,
		$\nu(x, B) = \nu_x(B) = P(\eta\in B|\xi = x)$,
		\[
		E(h(\eta)|\xi) = \psi(\xi), \quad \psi(x) = \int_{\mathbb{R}}h(y)\dd \nu_x(y).
		\]
	\item Transformation functions in product space,
		$\dd \mu(x_1, x_2) = \mu_1(\dd x_1)p(x_1, \dd x_2)$.
	\item Transformation functions = regular conditional distribution of given values.
	\item Fubini's theorem, computations (pay attention to the condition).
	\item Tulcea's theorem, the statement and applications.
\end{itemize}
